An Open Platform for Managing Short Programming Exercises

### 2013-06-25 paper/paper.tex
little more discussion, fixed acknowledgements

{\bf What is the right balance between short programming exercises and
  longer ``nifty'' assignments?}
Discuss.

{\bf What can we do to encourage students to use their time effectively outside of class?}

@@

This work was supported by a SIGCSE Special Projects grant (May 2012),
a York College Summer Research Fellowship (Summer 2013), [TODO: Knox College
grant], and [TODO: Amazon grant].

>>>>

{\bf What is the right balance between short programming exercises and
  longer ``nifty'' assignments?}
There has been a lot of work in the CS Education community developing
interesting and innovative introductory level programming assignments,
such as the wonderful examples presented each year at the ``Nifty Assignments'' panel at
SIGCSE.  Most introductory courses require at least a few
longer nifty-style programming assignments, in addition to shorter
programming homework assignments.  What is the proper balance between longer
nifty-style assignments and shorter, more focused programming exercises?  Is 
solving shorter programming exercises a pre-condition, or threshold skill, for
completing assignments?

{\bf Is the feedback provided by synchronous grading more effective
  than feedback from asynchronous grading?}
Faculty or Teaching Assistants who manually grade student programming
assignments can give detailed and customized feedback to
students, at the cost of some latency between the time the student
submits the assignment and the time they receive their grade and the
feedback.  Anecdotally, many faculty complain that students do not
seem to pay much attention to this feedback, possibly because those
points (marks) have already been lost and cannot be recovered.
While automated systems cannot give feedback that is as detailed as manual
grading, they can give feedback very quickly.

@@

This work was supported by a SIGCSE Special Projects grant (May 2012),
a York College Summer Research Fellowship (Summer 2013), an award from
the Paul K Richter and Evalyn E. Cook Richter Memorial Trusts at Knox
College, and an Amazon Web Services Teaching Grant.
